Clustering of Distributions on 1-Dimensional Manifolds

### 2021-10-06 scratch/distributions-on-1d-manifolds.Rmd
updated writeup

### General case

@@

>>>>

### Test for intersecting manifolds

\begin{theorem}
Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be two one-dimensional manifolds of unit length with $n_1$ and $n_2$ points drawn uniformly along them ($n = n_1 + n_2$).

Suppose we want to perform a hypothesis test for whether the ends of the manifolds meet. 
The $H_0$ is the case where $\delta = 0$ and $H_1$ is the case where $\delta > 0$. 
Define the test statistic $T_n = \|X_{(n_1)} - Y_{(1)}\|$ (or similar, depending on which ends meet). 
Then $T_n / 2 \stackrel{d}{\to} \Betadist(1, n)$ under $H_0$. 
\end{theorem}

## General case

@@

### Community detection for manifolds that emanate from the origin

### 2021-10-06 scratch/distributions-on-1d-manifolds.tex
updated writeup

\hypertarget{general-case}{%
\subsubsection{General case}\label{general-case}}

@@

>>>>

\hypertarget{test-for-intersecting-manifolds}{%
\subsubsection{Test for intersecting
manifolds}\label{test-for-intersecting-manifolds}}

\begin{theorem}
Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be two one-dimensional manifolds of unit length with $n_1$ and $n_2$ points drawn uniformly along them ($n = n_1 + n_2$).

Suppose we want to perform a hypothesis test for whether the ends of the manifolds meet. 
The $H_0$ is the case where $\delta = 0$ and $H_1$ is the case where $\delta > 0$. 
Define the test statistic $T_n = \|X_{(n_1)} - Y_{(1)}\|$ (or similar, depending on which ends meet). 
Then $T_n / 2 \stackrel{d}{\to} \mathrm{Beta}(1, n)$ under $H_0$. 
\end{theorem}

\hypertarget{general-case}{%
\subsection{General case}\label{general-case}}

@@

\hypertarget{community-detection-for-manifolds-that-emanate-from-the-origin}{%
\subsubsection{Community detection for manifolds that emanate from the
origin}\label{community-detection-for-manifolds-that-emanate-from-the-origin}}
